Rotations and Insecticide Resistance the story

### 2019-03-07 inst/documents/rotations_notes.Rmd
visualising mortality threshold

@@

>>>>

1/3/19

Had idea to try to plot regio of parameter space where mortality less than 90%.
Not sure it is very useful, but did make a start.

see plot_mort_thresh.r

5/3/19
~ added mort_or_freq switch to rotresist1/ui.r
~ added threshold to UI

7/3/19

Using mortality switch for sequences, currently it switches back to other insecticides even when they are below threshold.

Aha I think that is due to the min_rwr_interval. When it is set to 0 then the sim doesn't proceed.

~ struggled to add legend for green mortality lines
fixed now

@@

fix error
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 1e-04 , rot_interval = 10 , eff = 0.95 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0.01 , cost = 0.01 , logy = FALSE , no_r_below_start = FALSE , min_rwr_interval = 5 , threshold = 0.9 , mort_or_freq ='mort' )

~ rot_interval > 0
in insecticide_check()
Error in genotype_freq(rfreq) : 
  argument "rfreq" is missing, with no default

~ publish to shinyapps and send link to Ian

~ try to fix that min_rwr_interval seems to allow switching back to insecticides

~ check that per-diem for Geneva made it to my bank
